---
title: "Corona prepping using Finnish data CIBER"
author: "James Twose, Gjalt-Jorn Peters, Kaisa Sauro, Matti Heino & Nelli Hankonen"
date: "`r format(Sys.time(), '%H:%M:%S on %Y-%m-%d %Z (UTC%z)')`"
output:
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

Main question: at this point we're interested in one single classification, i.e. what predicts whether people do maskless contacts with non-householders

[Research Document](https://docs.google.com/document/d/1iLciHcvVvf8QwFS7wiyNBevpD1B9yDRqMlM4_oCcVcA/edit?usp=sharing)

[Questions codebook](https://docs.google.com/document/d/1YZVCP1UNxnNLAK2kYDfA9Y98leTZYurZD-d8iByhdi0/edit?usp=sharing)

[Method of delivery](https://docs.google.com/document/d/1G1JT9JUJrTK3aaXXuRawYACJaGNxU7mcXL9i-d8eKXY/edit)

[Question labels](https://docs.google.com/spreadsheets/d/1BEX4W8XRGnuDk4Asa_pdKij3EIZBvhSPqHxFrDjM07k/edit#gid=935884211)

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

# Setup {.tabset .tabset-pills}

## Overview

See the "Code and logs" tab for, well, the code and logs.

## Code and logs

```{r, check-packages, echo=FALSE, message=FALSE}

###-----------------------------------------------------------------------------
### I normally use 'ufs' for lots of small little functions including
### 'checkPkgs' which allows you to check for the presence of a package
### without loading it - this enforces use of the pkg::fun syntax, which
### is a bit safer (given that names are only unique within their namespace)
### and convenient if you end up writing a function you then port to a package
### (where you always use the :: operator for the former reason).
###-----------------------------------------------------------------------------

if (!('ufs' %in% installed.packages()[, 'Package'])) {
  install.packages("ufs");
}

ufs::checkPkgs("here");                  ### For relative paths
ufs::checkPkgs("googlesheets4");         ### For reading from Google Sheets
ufs::checkPkgs("openxlsx");              ### Reading/writing XLSX
ufs::checkPkgs("behaviorchange");        ### For the CIBER plots
ufs::checkPkgs("ggbeeswarm");            ### For beeswarms

### Potentially install dev version of behaviorchange
# ufs::quietGitLabUpdate("r-packages/behaviorchange@dev", quiet = FALSE);

###-----------------------------------------------------------------------------
### Packages to attach to the search path
###-----------------------------------------------------------------------------

# library(ggplot2)
# # library(parsnip)
# library(magrittr)
# library(dplyr)
# library(faux)
# library(DataExplorer)
# # library(caret)
# # library(randomForest)
# library(tidyr)
# # library(cvms)
# library(doParallel)
# # library(rattle)
# # library(rpart)
# source("coronapreppers_extras.R")

```

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

```{r, set-paths-and-urls}

###-----------------------------------------------------------------------------
### Setting paths and datafile name
###-----------------------------------------------------------------------------

basePath <- here::here();

dataPath <- file.path(basePath, "data");
figureDataPath <- file.path(basePath, "figure_data");
metadataPath <- file.path(basePath, "metadata");
outputPath <- file.path(basePath, "images");

dataFilename <- "shield_gjames_21-09-20.csv";

###-----------------------------------------------------------------------------
### Setting URLs and column names
###-----------------------------------------------------------------------------

questionLabels_sheetURL <-
  "https://docs.google.com/spreadsheets/d/1BEX4W8XRGnuDk4Asa_pdKij3EIZBvhSPqHxFrDjM07k";

questionLabels_varNameCol <- "New variable name";
questionLabels_leftAnchorCol <- "English lo-anchor";
questionLabels_rightAnchorCol <- "English hi-anchor";
questionLabels_labelCol <- "Label short"; # "Label";

```

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

```{r, load-data}

###-----------------------------------------------------------------------------
### Load data
###-----------------------------------------------------------------------------

#df <- read.csv("data/shield_gjames_21-06-10.csv")

### James: refactored a bit using paths defined above and to
### make this platform-independent
df <- df.raw <- read.csv(
  file.path(
    dataPath,
    dataFilename
  )
);

###-----------------------------------------------------------------------------
### Create new composite measure of intention and behavior
###-----------------------------------------------------------------------------

intentionVars <-
  grep("^intention_", names(df), value=TRUE);

### Note: intention response options are:
###   1 = I will wear a mask all the time
###   2 = I'm going to wear a mask part of the time
###   3 = I'm not going to wear a mask
###   4 = I'm not going to go at all
###
### We recode these so that the new categories reflect the
### risk due to potential unmasked exposure to SARS-CoV-2:
###   1 -> 0
###   2 -> 1
###   3 -> 2
###   4 -> 0

for (currentIntentionVar in intentionVars) {
  df[, paste0(currentIntentionVar, "_recoded")] <-
    ifelse(
      df[, currentIntentionVar] == 4,
      0,
      df[, currentIntentionVar] - 1
    );
}

df$intention_composite <-
  rowSums(df[, paste0(intentionVars, "_recoded")]);

### Behavior

behaviorVars <-
  grep("^behaviour_", names(df), value=TRUE);

behaviorVars_selected <-
  grep("indoors|unmasked", behaviorVars, value=TRUE);

### For these two behavior measures, the response
### options are different:
###
###   behaviour_indoors_nonhouseholders:
###     1 = Several times a day
###     2 = Every day
###     3 = 5-6 days
###     4 = 3-4 days
###     5 = 1-2 days
###     6 = Not at all
###
###   behaviour_unmasked:
###     1 = Every day
###     5-6 days
###     3-4 days
###     1-2 days
###     not at all
###
### These are recoded to ~ represent, respectively,
### 'mask wearing opportunities' and 'risk events'.

maskWearingOpportunities_recodingVector <-
  c(14/7, 1, 5.5/7, 3.5/7, 1.5/7, 0);

df[, paste0(behaviorVars_selected[1], "_recoded")] <-
  maskWearingOpportunities_recodingVector[
    df[, behaviorVars_selected[1]]
  ];

riskEvents_recodingVector <-
  c(1, 5.5/7, 3.5/7, 1.5/7, 0);

df[, paste0(behaviorVars_selected[2], "_recoded")] <-
  riskEvents_recodingVector[
    df[, behaviorVars_selected[2]]
  ];

df$behavior_composite <-
  df[, paste0(behaviorVars_selected[1], "_recoded")] *
  df[, paste0(behaviorVars_selected[2], "_recoded")];

df$behavior_composite_recoded <-
  df$behavior_composite * 5;

df$intention_behavior_composite <-
  rowMeans(
    df[,
       c('intention_composite',
         'behavior_composite_recoded')
      ],
    na.rm = TRUE);

### Invert the final measure so that higher scores represent the desirable
### behavior instead of the other way around.
df$intention_behavior_composite <-
  max(df$intention_behavior_composite, na.rm=TRUE) - 
  df$intention_behavior_composite;

###-----------------------------------------------------------------------------
### We now have two variables: a behavior composite that represents in which
### proportion of the situations where mask-wearing was the desirable behavior
### participants wore masks; and an intention-behavior composite, where this
### variable is averaged with intention.
###-----------------------------------------------------------------------------

### Use regular expressions to select variables:
###  - the | means "or";
###  - the ^ means "start of the text string"

determinantVars <- list(
  continuous =
    grep(
      
      ### We don't want intention as a determinant
      ### Also, leave out the SDT items because they're part of
      ### another study, and not easy to interpret as determinants
      ### as thet may measure two things.
      #   "^intention|^automaticity|attitude|^norms|^risk|^effective|^sdt",
      
      "^automaticity|attitude|^norms|^risk|^effective",
      
      names(df),
      value=TRUE
    ),
  dichotomous =
    grep(
      "barriers",
      names(df),
      value=TRUE
    )
);

### Superseded
#behaviorVarName <- "behaviour_unmasked";

### Using the new composite behavior measure
behaviorVarName <- "intention_behavior_composite";

#behaviorVarName_dichotomized <- "behaviour_unmasked_bool"; ### Redundant now
#
### Create dichotomized behavior measure
# df[, behaviorVarName_dichotomized] <-
#   ifelse(df[, behaviorVarName] < 5,
#          0,
#          1);

### Verify that
# table(df[, behaviorVarName],
#       df[, behaviorVarName_dichotomized]);

###-----------------------------------------------------------------------------
### Create factors for age and education
###-----------------------------------------------------------------------------

df$demographic_educationType <-
  ifelse(
    df$demographic_higher_education,
    "Theoretical",
    "Practical"
  );

df$demographic_educationType <-
  factor(
    df$demographic_educationType,
    levels = c("Practical", "Theoretical"),
    labels = c("Practical", "Theoretical"),
    ordered = TRUE
  );

ageRecodingVector <-
  c("18-29" = "Younger than 40",
    "30-39" = "Younger than 40",
    "40-49" = "40 to 59",
    "50-59" = "40 to 59",
    "60+" = "60 or older");

df$demographic_ageGroups <-
  ageRecodingVector[
    df$demographic_age
  ];

df$demographic_ageGroups <-
  factor(
    df$demographic_ageGroups,
    levels = unique(ageRecodingVector),
    labels = unique(ageRecodingVector),
    ordered=TRUE
  );

### Verify recoding

table(df$demographic_higher_education,
      df$demographic_educationType);

table(df$demographic_age,
      df$demographic_ageGroups);

### For convenience later on
ageGroups <- levels(df$demographic_ageGroups);
eduGroups <- levels(df$demographic_educationType);

###-----------------------------------------------------------------------------
### Export processed data
###-----------------------------------------------------------------------------

write.csv(
  df,
  file = file.path(
    dataPath,
    "data--preprocessed-for-CIBER.csv"
  )
);

```

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

```{r, load-labels}

###-----------------------------------------------------------------------------
### Load labels, store local backup, prepare vectors
###-----------------------------------------------------------------------------

questionLabels_localBackupFilename <-
  file.path(metadataPath, "questionLabels.xlsx");

### Use tryCatch in case we're offline
tryCatch({
  
  googlesheets4::gs4_deauth();
  
  questionLabelDf <-
    as.data.frame(
      googlesheets4::read_sheet(questionLabels_sheetURL)
    );
  
  ### Store local backup in case we're offline next time and so that it
  ### gets archived along with the rest if we freeze an OSF registration
  openxlsx::write.xlsx(
    questionLabelDf,
    questionLabels_localBackupFilename
  );
  
}, error = function(e) {
  
  ### We're probably offline; try reading local copy, otherwise throw error
  if (file.exists(questionLabels_localBackupFilename)) {
    questionLabelDf <-
      openxlsx::read.xlsx(
        questionLabels_localBackupFilename
      );
  } else {
    stop("I cannot read the google sheet with the question labels, nor ",
         "do I manage to read the spreadsheet from the local backup file.");
  }
  
});

###-----------------------------------------------------------------------------
### Create vectors
###-----------------------------------------------------------------------------

questionLabels <-
  stats::setNames(
    questionLabelDf[, questionLabels_labelCol],
    nm = questionLabelDf[, questionLabels_varNameCol]
  );

leftAnchors <-
  stats::setNames(
    questionLabelDf[, questionLabels_leftAnchorCol],
    nm = questionLabelDf[, questionLabels_varNameCol]
  );

rightAnchors <-
  stats::setNames(
    questionLabelDf[, questionLabels_rightAnchorCol],
    nm = questionLabelDf[, questionLabels_varNameCol]
  );

###-----------------------------------------------------------------------------
### Wrap vectors with labels
###-----------------------------------------------------------------------------

questionLabel_maxWidth <- 40;
anchors_maxWidth <- 20;

wrapVector <- function(x, width) {
  res <-
    unlist(
      lapply(
        strwrap(x, width = width, simplify = FALSE),
        paste,
        collapse = "\n"
      )
    );
  names(res) <- names(x);
  return(res);
}

questionLabels_wrapped <-
  wrapVector(questionLabels, questionLabel_maxWidth);

# questionLabels_wrapped <- questionLabels <-
#   stats::setNames(determinantVars$continuous,
#                   nm=determinantVars$continuous);

leftAnchors_wrapped <-
  wrapVector(leftAnchors, anchors_maxWidth);

rightAnchors_wrapped <-
  wrapVector(rightAnchors, anchors_maxWidth);

fullLabels <-
  stats::setNames(
    wrapVector(
      paste0(
        questionLabels,
        " [ ",
        leftAnchors[names(questionLabels)],
        " | ",
        rightAnchors[names(questionLabels)],
        " ]"
      ),
      questionLabel_maxWidth
    ),
    nm = names(questionLabels)
  );

```

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

```{r, set-parameters, eval=FALSE}

###-----------------------------------------------------------------------------
### Setting parameters (e.g. settings for the script etc)
###-----------------------------------------------------------------------------

grouping_var <- behaviorVarName
# feature_list <- colnames(df[, !(names(df) %in% c(grouping_var, "id"))])
feature_list <- c('intention_indoor_meeting', 'norms_people_present_indoors',
       'sdt_motivation_extrinsic_2', 'sdt_motivation_identified_4', 'norms_family_friends', 'norms_risk_groups', 'norms_officials',
       'norms_people_present_indoors')

```

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

```{r, eval=FALSE}

### James; deactivated this for now as this also happens just after the data
### were loaded. I assume this was a left-over from another script (like the
### 'commented out' loading of packages at the top), which also explains the
### approach that was chosen? Or maybe that's because this is Python-thinking
### expressed in R? :-)

if (grouping_var == "behaviour_unmasked") {
  # df <- df %>% mutate(tmp = if_else(!!as.symbol(grouping_var) != 5, 'bad', 'good'))
  df <- df %>% mutate(tmp = if_else(!!as.symbol(grouping_var) != 5, 0, 1))

  names(df)[names(df) == 'tmp'] <- paste0(grouping_var, "_bool")
}
    
```

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!-- At this point, we're done with the set-up                               -->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

```{r}
# df[, paste0(grouping_var, "_bool")] <- as.factor(df[, paste0(grouping_var, "_bool")])
```

```{r, eval=FALSE}
# df %<>%
#        mutate_each_(funs(factor(.)), colnames(df))
# str(df)

# ordinal_vars_mydata <- ordering_lookup %>% 
#   dplyr::filter(varname %in% names(df)) %>% 
#   dplyr::filter(ordering == "ordered")
#   
# df <- df %>% 
#   # Ordered variables as ordinal factors
#   dplyr::mutate(across(.cols = ordinal_vars_mydata$varname, 
#                         ~factor(., ordered = TRUE))) %>% 
#   # Everything else as unordered factors
#   dplyr::mutate(across(.cols = -ordinal_vars_mydata$varname, 
#                         ~factor(.))) %>% 
#   # Fix ordering in the intention variables
#   dplyr::mutate(across(.cols = contains("intention_"), 
#                         ~dplyr::recode_factor(.,
#                                               "1" = "4",
#                                               "2" = "1", 
#                                               "3" = "2",
#                                               "4" = "3",
#                                               .ordered = TRUE)))

str(df)

###-----------------------------------------------------------------------------
### @James: maybe use the fact that we already depend on dplyr anyway and use
### dplyr::glimpse here, instead of str?
###-----------------------------------------------------------------------------

```

```{r, fig.height=15, fig.width=15, eval=FALSE}
# Exploratory data analysis
plot_intro(df)
plot_bar(df)
plot_correlation(df)
```


```{r, eval=FALSE}
head(df[, c(paste0(grouping_var, "_bool"), grouping_var)])
```

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

# CIBER plots {.tabset .tabset-pills}

## Full sample

```{r, CIBER-behavior-full-sample}

### No longer necessary, set-up now happens above and distinguishes
### continuous and dichotomous variables

# tmp <- df %>%
#   select(-behaviour_unmasked_bool, -behaviour_unmasked, -id, -demographic_age) %>%
#   as.data.frame()
# 
# determinants_list <- colnames(tmp)

### Rescale variables to 0-1 --- note that the way this is done now
### assumes that the scale max is observed at least once. If that
### assumption doesn't hold, we may want to extract the scale max
### values from the google sheet with the labels.
df[, determinantVars$continuous] <-
  lapply(
    df[, determinantVars$continuous],
    function(x) {
      return((x - 1) / (max(x, na.rm=TRUE) - 1));
    }
  );

ciberJitterWidth <- floor(100*1/7) / 100;

CIBERplots <- list();

CIBERplots$fullSample <-
  behaviorchange::CIBER(
    data=df,
    determinants = determinantVars$continuous,
    targets = behaviorVarName,
    orderBy = behaviorVarName,
    titleVarLabels = stats::setNames("mask wearing", nm=behaviorVarName),
    titleSuffix = "(full sample)",
    subQuestions = questionLabels_wrapped[determinantVars$continuous],
    leftAnchors = leftAnchors_wrapped[determinantVars$continuous],
    rightAnchors = rightAnchors_wrapped[determinantVars$continuous],
    jitterWidth = ciberJitterWidth,
    drawPlot = FALSE,
    returnPlotOnly = FALSE
  );

ufs::knitAndSave(
  CIBERplots$fullSample$output$plot,
  figCaption = paste0("CIBER plot for the full sample."),
  path = outputPath,
  figWidth = attr(CIBERplots$fullSample$output$plot, "width"),
  figHeight = attr(CIBERplots$fullSample$output$plot, "height"),
);

```

```{r, CIBER-behavior-per-subgroup, results="asis"}

### Age

for (currentAgeGroup in levels(df$demographic_ageGroups)) {
  
  ufs::heading(currentAgeGroup,
               headingLevel = 2);

  CIBERplots[[currentAgeGroup]] <-
    behaviorchange::CIBER(
      data = df[df$demographic_ageGroups == currentAgeGroup, ],
      determinants = determinantVars$continuous,
      targets = behaviorVarName,
      orderBy = behaviorVarName,
      titleVarLabels = stats::setNames("mask wearing", nm=behaviorVarName),
      titleSuffix = paste0("(", currentAgeGroup, ")"),
      subQuestions = questionLabels_wrapped[determinantVars$continuous],
      leftAnchors = leftAnchors_wrapped[determinantVars$continuous],
      rightAnchors = rightAnchors_wrapped[determinantVars$continuous],
      jitterWidth = ciberJitterWidth,
      drawPlot = FALSE,
      returnPlotOnly = FALSE
    );

  ### Use `cat` as R inhibits output in for-loops
  cat(
    ufs::knitAndSave(
      CIBERplots[[currentAgeGroup]]$output$plot,
      figCaption = paste0("CIBER plot for age group: ", currentAgeGroup, "."),
      path = outputPath,
      figWidth = attr(CIBERplots[[currentAgeGroup]]$output$plot, "width"),
      figHeight = attr(CIBERplots[[currentAgeGroup]]$output$plot, "height"),
    )
  );
  
}

### Education

for (currentEduGroup in levels(df$demographic_educationType)) {
    
  ufs::heading(currentEduGroup,
               headingLevel = 2);

  CIBERplots[[currentEduGroup]] <-
    behaviorchange::CIBER(
      data = df[df$demographic_educationType == currentEduGroup, ],
      determinants = determinantVars$continuous,
      targets = behaviorVarName,
      orderBy = behaviorVarName,
      titleVarLabels = stats::setNames("mask wearing", nm=behaviorVarName),
      titleSuffix = paste0("(", currentEduGroup, ")"),
      subQuestions = questionLabels_wrapped[determinantVars$continuous],
      leftAnchors = leftAnchors_wrapped[determinantVars$continuous],
      rightAnchors = rightAnchors_wrapped[determinantVars$continuous],
      jitterWidth = ciberJitterWidth,
      drawPlot = FALSE,
      returnPlotOnly = FALSE
    );

  ### Use `cat` as R inhibits output in for-loops
  cat(
    ufs::knitAndSave(
      CIBERplots[[currentEduGroup]]$output$plot,
      figCaption = paste0("CIBER plot for education group: ", currentEduGroup, "."),
      path = outputPath,
      figWidth = attr(CIBERplots[[currentEduGroup]]$output$plot, "width"),
      figHeight = attr(CIBERplots[[currentEduGroup]]$output$plot, "height"),
    )
  );
 
}

```

```{r, CIBER-dichotomized-behavior, eval=FALSE}

### Chunk set to eval=FALSE since we no longer look at this

# CIBERplots$dichotomized_behavior <-
#   behaviorchange::CIBER(
#     data=df,
#     determinants = determinantVars$continuous,
#     targets = behaviorVarName_dichotomized,
#     orderBy = behaviorVarName_dichotomized,
#     subQuestions = questionLabels_wrapped[determinantVars$continuous],
#     leftAnchors = leftAnchors_wrapped[determinantVars$continuous],
#     rightAnchors = rightAnchors_wrapped[determinantVars$continuous],
#     drawPlot = FALSE
#   );
# 
# ufs::knitAndSave(
#   CIBERplots$dichotomized_behavior,
#   figCaption = paste0("CIBER plot for dichotomized behavior measure; ",
#                       "note that the right-hand panel shows the ",
#                       "point-biserial correlation, not the ",
#                       "Pearson correlation."),
#   path = outputPath,
#   figWidth = attr(CIBERplots$dichotomized_behavior, "width"),
#   figHeight = attr(CIBERplots$dichotomized_behavior, "height"),
# );

### ufs::knitAndSave both knits and, well, saves :-)
# ggsave("CIBER_plot_boolean.png", dpi = 400)

```

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

# Potential for Change Indices {.tabset .tabset-pills}

Note: until we standardize the scales, these are incomparable, as they use the 'room for improvement' which is scale-dependent (i.e. it will always be smaller for a dichotomous variable).

## Full sample

```{r, potential-for-change-index}

df_standardized <- df;

df_standardized[, determinantVars$continuous] <-
  lapply(
    df_standardized[, determinantVars$continuous],
    function(x) {
      lowestObservation <- min(x, na.rm = TRUE);
      highestObservation <- max(x, na.rm = TRUE);
      return(
        (x - lowestObservation) / highestObservation
      );
    }
  );

dstList <- list();

dstList$fullSample <-
  behaviorchange::determinant_selection_table(
    data=df_standardized,
    determinants = determinantVars$continuous,
    determinantLabels =
      paste0(questionLabels_wrapped[determinantVars$continuous],
             " [ ",
             leftAnchors_wrapped[determinantVars$continuous],
             " | ",
             rightAnchors_wrapped[determinantVars$continuous],
             " ]"),
    target = behaviorVarName,
    sortBy = 6
  );

print(dstList$fullSample);

```

```{r, potential-for-change-index-per-subgroup, results="asis"}

### Age

for (currentAgeGroup in levels(df$demographic_ageGroups)) {
  
  ufs::heading(currentAgeGroup,
               headingLevel = 2);

  dstList[[currentAgeGroup]] <-
    behaviorchange::determinant_selection_table(
      data=df_standardized[
        df_standardized$demographic_ageGroups == currentAgeGroup,
      ],
      determinants = determinantVars$continuous,
      determinantLabels =
        paste0(questionLabels_wrapped[determinantVars$continuous],
               " [ ",
               leftAnchors_wrapped[determinantVars$continuous],
               " | ",
               rightAnchors_wrapped[determinantVars$continuous],
               " ]"),
      target = behaviorVarName,
      sortBy = 6,
      headingLevel = 3
    );
      
  print(
    behaviorchange:::knit_print.determinantSelectionTable(
      dstList[[currentAgeGroup]],
      render_preview = FALSE
    )
  );

}

### Education

for (currentEduGroup in levels(df$demographic_educationType)) {
    
  ufs::heading(currentEduGroup,
               headingLevel = 2);

  dstList[[currentEduGroup]] <-
    behaviorchange::determinant_selection_table(
      data=df_standardized[
        df_standardized$demographic_educationType == currentEduGroup,
      ],
      determinants = determinantVars$continuous,
      determinantLabels =
        paste0(questionLabels_wrapped[determinantVars$continuous],
               " [ ",
               leftAnchors_wrapped[determinantVars$continuous],
               " | ",
               rightAnchors_wrapped[determinantVars$continuous],
               " ]"),
      target = behaviorVarName,
      sortBy = 6,
      headingLevel = 3
    );
  
  print(
    behaviorchange:::knit_print.determinantSelectionTable(
      dstList[[currentEduGroup]],
      render_preview = FALSE
    )
  );

}

```

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

```{r, export-aggregated-results}

for (sampleName in names(dstList)) {
  
  write.csv(
    dstList[[sampleName]],
    file.path(
      figureDataPath,
      paste0(
        "determinant-selection-table-",
        sampleName,
        ".csv")
      ),
    row.names = FALSE
  );
  
  ### CIBERplots has the same names
  tmpDf <- CIBERplots[[sampleName]]$intermediate$meansDat;
  names(tmpDf)[1:3] <- c("mean_ci_lo", "mean_point", "mean_ci_hi");
  row.names(tmpDf) <- tmpDf$label;
  tmpDf[tmpDf$label, c("r_ci_lo", "r_point", "r_ci_hi")] <-
    CIBERplots[[sampleName]]$intermediate$assocDat[[1]][tmpDf$label, ];
  tmpDf$fullLabel <-
    fullLabels[tmpDf$label];
  
  write.csv(
    tmpDf,
    file.path(
      figureDataPath,
      paste0(
        "CIBER-plot-data-",
        sampleName,
        ".csv")
      ),
    row.names = FALSE
  );
  
}

```

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

# SHAP plots {.tabset .tabset-pills}

```{r, results="asis"}

sampleLabels <-
  c(
    fullSample = "Full sample",
    `Practical` = "Education: practical",
    `Theoretical` = "Education: theoretical",
    `Younger than 40` = "Age: 18-39",
    `40 to 59` = "Age: 40-59",
    `60 or older` = "Age: 60+"
  );

shapFilenames <-
  c(
    fullSample = file.path(figureDataPath,
                           "All_shap_real_values.csv"),
    `Practical` = file.path(figureDataPath,
                            "Lower_Education_shap_real_values.csv"),
    `Theoretical` = file.path(figureDataPath,
                              "Higher_Education_shap_real_values.csv"),
    `Younger than 40` = file.path(figureDataPath,
                                  "18 - 39_shap_real_values.csv"),
    `40 to 59` = file.path(figureDataPath,
                           "40 - 59_shap_real_values.csv"),
    `60 or older` = file.path(figureDataPath,
                              "60+_shap_real_values.csv")
  );

shapDfs <-
  stats::setNames(
    lapply(
      shapFilenames,
      read.csv
    ),
    names(shapFilenames)
  );

shapDfs <-
  lapply(
    shapDfs,
    function(currentDf) {
      currentDf$label <-
        fullLabels[currentDf$variable];
      ### Reverse order because ggplot plots from bottom to top on Y axis
      currentDf$label <-
        factor(
          currentDf$label,
          levels = rev(unique(fullLabels[currentDf$variable])),
          ordered = TRUE
        );
      ### Store actual_value as factor, too
      currentDf$actualValue_factor <-
        factor(
          currentDf$actual_value,
          levels = seq(min(currentDf$actual_value, na.rm=TRUE),
                       max(currentDf$actual_value, na.rm=TRUE)),
          ordered = TRUE
        );
      return(currentDf);
    }
  );

shapPlots <-
  stats::setNames(
    lapply(
      names(shapDfs),
      function(currentSample) {
        return(
          ggplot2::ggplot(
            data = shapDfs[[currentSample]],
            mapping = ggplot2::aes_string(
              x = "shap_value",
              y = "label",
              fill = "actualValue_factor",
              color = "actualValue_factor"
            )
          ) +
            ggbeeswarm::geom_beeswarm(
              size = 2,
              alpha = .66
            ) +
            ggplot2::theme_minimal() +
            ggplot2::labs(title = sampleLabels[currentSample],
                          x = "SHAP Value",
                          y = NULL,
                          fill = "Score",
                          color = "Score")
        );
      }
    ),
    nm = names(shapDfs)
  );

for (currentSample in names(shapPlots)) {
  ufs::heading(sampleLabels[currentSample],
               headingLevel = 2);
  cat(
    ufs::knitAndSave(
      shapPlots[[currentSample]],
      path = outputPath,
      figCaption = paste0("SHAP values for ", sampleLabels[currentSample]),
      figWidth = 9,
      figHeight = 14
    )
  );
}

```

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

# Combined plots {.tabset .tabset-pills}

```{r, combined-plots, results="asis"}

widths <- c(.8, .2);
plotWidths = 12;
plotHeights = 13;

for (i in names(CIBERplots)) {

  ufs::heading(i, headingLevel = 2);
  
  ufs::knitAndSave(
    patchwork::wrap_plots(CIBERplots[[i]]$output$plot,
                          shapPlots[[i]],
                          widths = widths),
    path = outputPath,
    figCaption = paste0("Combined plots for ", i),
    figWidth = plotWidths,
    figHeight = plotHeights
  )
  
}

```

<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->
<!----------------------------------------------------------------------------->

# Session information

```{r, session-info}
utils::sessionInfo();
```
