---
title: "Corona prepping using Finnish data Decision Trees"
author: "James Twose"
output: html_notebook
---

Main question: at this point we're interested in one single classification, i.e. what predicts whether people do maskless contacts with non-householders

[Research Document](https://docs.google.com/document/d/1iLciHcvVvf8QwFS7wiyNBevpD1B9yDRqMlM4_oCcVcA/edit?usp=sharing)

[Questions codebook](https://docs.google.com/document/d/1YZVCP1UNxnNLAK2kYDfA9Y98leTZYurZD-d8iByhdi0/edit?usp=sharing)

[Method of delivery](https://docs.google.com/document/d/1G1JT9JUJrTK3aaXXuRawYACJaGNxU7mcXL9i-d8eKXY/edit)

```{r, echo=FALSE, message=FALSE}
library(ggplot2)
library(parsnip)
library(magrittr)
library(dplyr)
library(faux)
library(DataExplorer)
library(caret)
library(randomForest)
library(tidyr)
library(cvms)
library(doParallel)
library(rattle)
library(rpart)

library(tidyverse)

# devtools::install_github('ModelOriented/treeshap')

```

```{r}
sessionInfo()
getwd()
```

# Data preparation

```{r}
df <- read.csv("../../data/taloustutkimus/shield_gjames_21-06-10.csv")
```

```{r}
grouping_var <- "behaviour_unmasked"
# feature_list <- colnames(df[, !(names(df) %in% c(grouping_var, "id"))])
feature_list <- c('intention_indoor_meeting', 'norms_people_present_indoors',
       'sdt_motivation_extrinsic_2', 'sdt_motivation_identified_4', 'norms_family_friends', 'norms_risk_groups', 'norms_officials',
       'norms_people_present_indoors')
```

```{r}
if (grouping_var == "behaviour_unmasked") {
  # df <- df %>% mutate(tmp = if_else(!!as.symbol(grouping_var) != 5, 'bad', 'good'))
  df <- df %>% mutate(tmp = if_else(!!as.symbol(grouping_var) != 5, 0, 1))

  names(df)[names(df) == 'tmp'] <- paste0(grouping_var, "_bool")
}
    
```

```{r}
df[, paste0(grouping_var, "_bool")] <- as.factor(df[, paste0(grouping_var, "_bool")])
```

## Wrangle ordered and unordered factors

Create dataframe with the appropriate measurement scales (from: <https://docs.google.com/spreadsheets/d/1BEX4W8XRGnuDk4Asa_pdKij3EIZBvhSPqHxFrDjM07k/edit#gid=935884211>)

```{r}
ordering_lookup <- data.frame(
  varname = c("demographic_id", "demographic_gender", "demographic_age", "demographic_region", "demographic_4_areas", "demographic_8_areas", "demographic_education", "demographic_profession", "demographic_household_stage", "demographic_household_size", "demographic_household_income", "demographic_apartment_type", "behaviour_indoors_nonhouseholders", "behaviour_close_contact", "behaviour_quarantined", "behaviour_unmasked", "mask_wearing_cloth_mask", "mask_wearing_disposable_mask", "mask_wearing_certified_mask", "mask_wearing_ffp2", "mask_wearing_vizire", "mask_wearing_none", "mask_wearing_other", "mask_wearing_reuse", "intention_store", "intention_public_transport", "intention_indoor_meeting", "intention_restaurant", "intention_pa", "automaticity_carry_mask", "automaticity_put_on_mask", "post_covid_maskwearing_if_reccd", "inst_attitude_protects_self", "inst_attitude_protects_others", "inst_attitude_sense_of_community", "inst_attitude_enough_oxygen", "inst_attitude_no_needless_waste", "norms_family_friends", "norms_risk_groups", "norms_officials", "norms_people_present_indoors", "aff_attitude_comfortable", "aff_attitude_calm", "aff_attitude_safe", "aff_attitude_responsible", "aff_attitude_difficult_breathing", "barriers_nothing", "barriers_money", "barriers_forget_carry", "barriers_forget_wear", "barriers_group_pressure", "barriers_medical_symptoms", "barriers_skin", "barriers_difficult_breathing", "barriers_eyeglasses_fog", "barriers_raspyvoice", "barriers_headache", "barriers_drymouth", "barriers_earpain", "barriers_general_uncomfy", "barriers_other", "effective_means_handwashing", "effective_means_masks", "effective_means_distance", "effective_means_ventilation", "risk_likely_contagion", "risk_contagion_absent_protection", "risk_severity", "risk_fear_spread", "risk_fear_contagion_self", "risk_fear_contagion_others", "risk_fear_restrictions", "sdt_needs_autonomy_1", "sdt_needs_competence_1", "sdt_needs_relatedness_1", "sdt_needs_autonomy_2", "sdt_needs_competence_2", "sdt_needs_relatedness_2", "sdt_motivation_extrinsic1", "sdt_motivation_amotivation_1", "sdt_motivation_identified_1", "sdt_motivation_introjected_1", "sdt_motivation_extrinsic_2", "sdt_motivation_introjected_2", "sdt_motivation_amotivation_2", "sdt_motivation_extrinsic_3", "sdt_motivation_identified_2", "sdt_motivation_identified_3", "sdt_motivation_identified_4", "sdt_motivation_amotivation_3", "sdt_motivation_introjected_3", "attention_check", "vaccination_status_intention_self", "vaccination_status_closeones", "covid_tested", "had_covid", "demographic_risk_group", "needprotection_before_shots", "needprotection_after_1_shot", "needprotection_after_2_shots", "children_age_groups"),
  ordering = c("unordered", "mixed", "ordered", "unordered", "unordered", "unordered", "mixed", "unordered", "unordered", "mixed", "mixed", "unordered", "ordered", "ordered", "unordered", "ordered", "unordered", "unordered", "unordered", "unordered", "unordered", "unordered", "unordered", "mixed", "mixed", "mixed", "mixed", "mixed", "mixed", "ordered", "ordered", "unordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "unordered", "unordered", "unordered", "unordered", "unordered", "unordered", "unordered", "unordered", "unordered", "unordered", "unordered", "unordered", "unordered", "unordered", "unordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "ordered", "unordered", "ordered", "unordered", "ordered", "unordered", "ordered", "ordered", "ordered", "unordered")
)

```

```{r}

ordinal_vars_mydata <- ordering_lookup %>% 
  dplyr::filter(varname %in% names(df)) %>% 
  dplyr::filter(ordering == "ordered")
  
df <- df %>% 
  # Ordered variables as ordinal factors
  dplyr::mutate(across(.cols = ordinal_vars_mydata$varname, 
                        ~factor(., ordered = TRUE))) %>% 
  # Everything else as unordered factors
  dplyr::mutate(across(.cols = -ordinal_vars_mydata$varname, 
                        ~factor(.))) %>% 
  # Fix ordering in the intention variables
  dplyr::mutate(across(.cols = contains("intention_"), 
                        ~dplyr::recode_factor(.,
                                              "1" = "4",
                                              "2" = "1", 
                                              "3" = "2",
                                              "4" = "3",
                                              .ordered = TRUE))) %>%
  na.omit()


```

```{r, fig.height=15, fig.width=15}
# Exploratory data analysis
DataExplorer::plot_intro(df)
DataExplorer::plot_bar(df)
DataExplorer::plot_correlation(df)
```

```{r}
head(df[, c(paste0(grouping_var, "_bool"), grouping_var)])
```

```{r}
x <- df %>%
  dplyr::mutate(target = dplyr::case_when(
      # at least part of the time intends to wear a mask, or doesn't go at all
      intention_indoor_meeting != 3 & 
        # didn't have maskless contacts during 7 days 
        behaviour_unmasked >= 4 ~ 
        "High_masking",
      TRUE ~ "Low_masking")) %>% 
  select(-contains("behaviour"),
         -contains("intention"),
         -id) %>%
  as.data.frame() %>% 
  na.omit()

y <- x %>% 
  dplyr::select(target) %>% 
  dplyr::pull()

x <- x %>% dplyr::select(-target)
```

```{r}
set.seed(2021)
inTrain <- createDataPartition(y, p = .80, list = FALSE)[,1]

x_train <- x[ inTrain, ]
x_test  <- x[-inTrain, ]

y_train <- y[ inTrain]
y_test  <- y[-inTrain]

# colnames(x_train)
```

# FFT

## Age groups

```{r}
fft_train <- data.frame(x_train, target = y_train) %>% 
  dplyr::mutate(target = dplyr::case_when(target == "Low_masking" ~ FALSE,
                                          target == "High_masking" ~ TRUE)) # %>% 
  # dplyr::select(-contains("behaviour"),
  #               -contains("mask_wearing"),
  #               -contains("barrier"))

fft_test <- data.frame(x_test, target = y_test) %>% 
  dplyr::mutate(target = dplyr::case_when(target == "Low_masking" ~ FALSE,
                                          target == "High_masking" ~ TRUE)) # %>% 
  # dplyr::select(-contains("behaviour"),
  #               -contains("mask_wearing"),
  #               -contains("barrier"))

cl <- makePSOCKcluster(8)
registerDoParallel(cl)

set.seed(2021)

fft_agegroup <- list(c("18-29", "30-39", "40-49", "50-59", "60+"),
                     c("60+"), 
                     c("40-49", "50-59"), 
                     c("18-29", "30-39"))

results_fft <- list()

for (i in 1:length(fft_agegroup)){
results_fft[[i]] <- FFTrees::FFTrees(formula = target ~ ., 
                     data = fft_train %>% 
                       dplyr::filter(demographic_age %in% fft_agegroup[[i]]),  
                     data.test = fft_test %>% 
                       dplyr::filter(demographic_age %in% fft_agegroup[[i]]),
                     algorithm = "ifan", #"dfan",
                     do.comp = TRUE,
                     decision.labels = c("Lower masking", "Higher masking"))
}
  stopCluster(cl)

for (i in 1:length(fft_agegroup)){
plot(results_fft[[i]],   
     # tree = i,
     main = paste("Age groups:", 
                  paste(fft_agegroup[[i]], collapse = ", "),
                  collapse = ""),
     # decision.labels = c("Adequate_masking", "Improvable"),
     data = "test")
}
  
```

## Gender

```{r}
# fft_train <- data.frame(x_train, target = y_train) %>% 
#   dplyr::mutate(target = dplyr::case_when(target == 0 ~ FALSE,
#                                           target == 1 ~ TRUE)) # %>% 
#   # dplyr::select(-contains("behaviour"),
#   #               -contains("mask_wearing"),
#   #               -contains("barrier"))
# 
# fft_test <- data.frame(x_test, target = y_test) %>% 
#   dplyr::mutate(target = dplyr::case_when(target == 0 ~ FALSE,
#                                           target == 1 ~ TRUE)) # %>% 
#   # dplyr::select(-contains("behaviour"),
#   #               -contains("mask_wearing"),
#   #               -contains("barrier"))

cl <- makePSOCKcluster(8)
registerDoParallel(cl)

set.seed(2021)

fft_gender <- unique(fft_train$demographic_gender)

results_fft <- list()

for (i in fft_gender){
results_fft[[i]] <- FFTrees::FFTrees(formula = target ~ ., 
                     data = fft_train %>% 
                       dplyr::filter(demographic_gender == fft_gender[[i]]),  
                     data.test = fft_test %>% 
                       dplyr::filter(demographic_gender == fft_gender[[i]]),
                     algorithm = "ifan", #"dfan",
                     do.comp = TRUE,
                     decision.labels = c("Lower masking", "Higher masking"))
}
  stopCluster(cl)

for (i in 1:length(fft_gender)){
plot(results_fft[[i]],   
     # tree = i,
     main = paste("Gender:", 
                  paste(fft_gender[[i]], collapse = ", "),
                  collapse = ""),
     # decision.labels = c("Adequate_masking", "Improvable"),
     data = "test")
}
  
```

```{r}
attr(df_categories$sdt_needs_relatedness_1, "label")

attr(df_categories$sdt_motivation_extrinsic_2, "labels")

attr(df_categories$post_covid_maskwearing_if_reccd, "labels")

```

# Running an ordinal variant of a decision tree (rpartScore) using the top features found, with a grid search CV

```{r}
# # Define the control using a random forest selection function
# control <- rfeControl(functions = rfFuncs, # random forest
#                       method = "repeatedcv", # or just cv
#                       repeats = 10, # number of repeats
#                       number = 10) # the number of folds
```

```{r}
start_time <- Sys.time()

cl <- parallel::makePSOCKcluster(8)
doParallel::registerDoParallel(cl)

set.seed(2021)


# Specify 10 fold cross-validation
ctrl_cv <- trainControl(method = "repeatedcv",
                        search = "grid",
                        number = 10,
                        repeats = 10,
                        timingSamps = 5,
                        # seeds = c(1:101)
                        )

dectree_group <- list(c("18-29", "30-39", "40-49", "50-59", "60+"),
                      c("60+"), 
                      c("40-49", "50-59"), 
                      c("18-29", "30-39"))

dec_mod <- list()
xdata <- list()
xdata_balanced <- list()
ydata <- list()
xdata_balanced_notarget <- list()

for (i in 1:length(dectree_group)){
  
  xdata[[i]] <- data.frame(x_train, target = y_train) %>% 
    dplyr::filter(demographic_age %in% dectree_group[[i]]) 
  
  # Under- and oversampling to balance data
  xdata_balanced[[i]] <- 
    ROSE::ovun.sample(formula = target ~ ., 
                      data = xdata[[i]],
                      p = 0.5,
                      seed = 1,
                      method = "both")$data 
  
  ydata[[i]] <- xdata_balanced[[i]] %>% 
    dplyr::select(target) %>% 
    dplyr::pull()
  
  xdata_balanced_notarget[[i]] <- xdata_balanced[[i]] %>% 
    dplyr::select(-target)


  # Predict mask wearing using decision tree
  dec_mod[[i]] <- caret::train(x = xdata_balanced_notarget[[i]],
                        y = ydata[[i]],
                        method = "rpartScore",  
                        trControl = ctrl_cv,
                        tuneGrid = expand.grid(
                          # "by" used to be 0.1
                          cp = seq(from = 0, to = 1, by = 0.05),
                          split = c("abs", "quad"),
                          prune = c("mc", "mr")
                        )
  )
}

parallel::stopCluster(cl)

end_time <- Sys.time()
end_time - start_time
```

```{r}
foreach::registerDoSEQ()
```

```{r}
target_balances <- list()

for (i in 1:length(dectree_group)){
target_balances[[i]] <- xdata_balanced[[i]] %>% 
  dplyr::filter(demographic_age %in% dectree_group[[i]]) %>% 
    pull(target) %>% 
  table()
}

target_balances
```



```{r}
varimp_data <- purrr::map(.x = dec_mod,
                          .f = caret::varImp)

varimp_data_viz <- purrr::map(.x = varimp_data,
                              .f = ~.x[[1]] %>% 
                                tibble::rownames_to_column(var = "Variable")) 
                             
varimp_data_viz_ordered <- 
  purrr::map(.x = varimp_data_viz,
             .f = ~.x %>% 
               dplyr::mutate(Variable = 
                               forcats::fct_reorder(Variable, Overall)))
             
# Use to match a subset's variable order to that of the whole group 
order_to_match <- varimp_data_viz_ordered[[1]]$Variable

varimp_plots_groups <- purrr::map2(.x = varimp_data_viz_ordered,
            .y = dectree_group,
            .f = ~.x %>% 
              # # Matching order with that of the whole group is messy; omit.
              # dplyr::mutate(Variable = factor(Variable, 
              #                                 levels = rev(order_to_match))) %>% 
              ggplot(aes(y = Variable,
                         x = Overall,
                         fill = Overall)) +
              geom_bar(stat = "identity", position = "dodge") +
              labs(x = "Importance",
                   title = paste("Age groups:", 
                                 paste(.y, collapse = ", "),
                                 collapse = "")) +
              
              theme_bw() +
              guides(fill = FALSE) +
              scale_fill_viridis_c(option = "inferno",
                                   end = 0.8))


for (i in 1:length(varimp_plots_groups)) {
              ggsave(filename = paste0("variable_importance_dectree_", 
                                       paste(dectree_group[[i]], collapse = "_"),
                                       ".png"), 
                     plot = varimp_plots_groups[[i]],
                     width = 14, 
                     height = 14)
}

```

## Differences in variable importance compared to full data

```{r}
# Renaming columns to reflect groups
new_varnames <- purrr::map(.x = dectree_group,
                           .f = ~paste(.x, collapse = ", "))

new_varnames[[1]] <- "All ages"

varimp_renamed <- purrr::map2(.x = varimp_data_viz_ordered,
           .y = new_varnames,
           .f = ~.x %>% 
             # https://stackoverflow.com/a/46616742
             dplyr::rename(!!.y := Overall))

# Merge the data frames with different age groups
varimp_renamed_joined <- varimp_renamed %>% 
  purrr::reduce(left_join, by = "Variable")

percentile_dropped <- 20

varimp_renamed_joined_dropped <- varimp_renamed_joined %>% 
  dplyr::mutate(importance_sum = rowSums(across(where(is.numeric)))) %>% 
  # Drop the values that are not important in any of the groups
  filter(`All ages` > quantile(importance_sum, percentile_dropped/100)) 

# Calculate differences from importances in full dataset
varimp_renamed_joined_diff <- varimp_renamed_joined_dropped %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(across(-c("Variable", `All ages`, importance_sum),
                ~. - `All ages`,
                .names = "{.col}_diff")) %>% 
  dplyr::ungroup()

varimp_diff_viz <- varimp_renamed_joined_diff %>% 
  dplyr::mutate(ordering = `All ages`) %>%
  tidyr::pivot_longer(c(`All ages`, contains("_diff")),
                      names_to = "Group",
                      values_to = "importance_diff") %>% 
  # dplyr::mutate(Variable = paste0(Variable, 
  #                                 " (", 
  #                                 round(`All ages`, digits = 0),
  #                                 ")")) %>% 
  # # For plotting, order the variables according to...
  # dplyr::group_by(Variable) %>% 
  # dplyr::mutate(ordering = sum(abs(importance_diff))) %>% 
  # dplyr::ungroup() %>%
  # Reorder by previously defined rule
  dplyr::mutate(Variable = forcats::fct_reorder(Variable, abs(ordering))) %>% 
  dplyr::mutate(Group = stringr::str_remove(string = Group,
                                            pattern = "_diff")) %>% 
  dplyr::select(Variable, Group, importance_diff) 

# head(varimp_diff_viz)

varimp_diff_viz_with_aggregate_importance <- dplyr::left_join(
  x = varimp_diff_viz,
  y = varimp_renamed_joined %>% 
    dplyr::select(Variable, aggregate_importance = `All ages`),
  by = "Variable")
```

### Make plots

```{r}
plot_varimp_subgroup_diffs <- varimp_diff_viz_with_aggregate_importance %>%
  dplyr::filter(stringr::str_detect(string = Variable,
                                    pattern = "demographic_age",
                                    negate = TRUE)) %>%
  dplyr::filter(Group != "All ages") %>% 
  ggplot(aes(y = Variable,
             x = importance_diff,
             fill = importance_diff)) +
  geom_bar(stat = "identity", position = "dodge") +
  # # Point indicating aggregate importance; not very clear 
  # geom_point(aes(x = 0,
  #                y = Variable,
  #                fill = aggregate_importance,
  #                size = aggregate_importance,
  #                alpha = 0.5)) +
  labs(x = "Difference in importance",
       y = NULL) +
  theme_bw() +
  guides(fill = FALSE,
         size = FALSE,
         alpha = FALSE) +
  scale_fill_viridis_c(option = "inferno",
                       end = 0.8) +
  theme(text = element_text(size = 20)) +
  facet_wrap(~Group, 
             #ncol = 3
             )

plot_varimp_aggregate_absolutes <- varimp_diff_viz_with_aggregate_importance %>%
  dplyr::filter(stringr::str_detect(string = Variable,
                                    pattern = "demographic_age",
                                    negate = TRUE)) %>%
  dplyr::filter(Group == "All ages") %>% 
  ggplot(aes(y = Variable,
             x = importance_diff,
             fill = importance_diff)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Absolute importance",
       y = NULL,
       caption = paste0(
  "- Zero values indicate importance is equal to that of full group.\n",
  "- Positive (negative) values indicate variable is ",
  "more (less) important in subgroup.\n",
  # "- Size of ball represents importance",
  # "in the model with full population.\n",
  "- ", percentile_dropped,
  " percent of variables with smallest importance values omitted.\n"
  # "- Variables are ordered by ",
  # "sum of absolute values of differences from population value."
  )
       ) +
  theme_bw() +
  guides(fill = FALSE,
         size = FALSE,
         alpha = FALSE) +
  scale_fill_viridis_c(option = "inferno",
                       end = 0.8) +
  theme(text = element_text(size = 20)) +
  facet_wrap(~Group, 
             #ncol = 3
             )

cowplot::plot_grid(plot_varimp_subgroup_diffs, 
                   plot_varimp_aggregate_absolutes +
                     theme(axis.text.y = element_blank(),
                           axis.line.y = element_blank(),
                           axis.title.y= element_blank(),
                           axis.ticks.y= element_blank()),
                   nrow = 1,
                   rel_widths = c(3, 1),
                   align = 'h', axis = 'tb')

ggsave(filename = "plot_of_differences.png", 
       width = 14, 
       height = 14)

```


```{r}
for(i in 1:length(dec_mod)){
  print(dec_mod[[i]]$results)
}
```

## Post prediction

```{r}

xdata_test <- list()
ydata_test <- list()
xdata_test_notarget <- list()

for (i in 1:length(dectree_group)){
  
  xdata_test[[i]] <- data.frame(x_test, target = y_test) %>% 
    dplyr::filter(demographic_age %in% dectree_group[[i]]) 

  ydata_test[[i]] <- xdata_test[[i]] %>% 
    dplyr::select(target) %>% 
    dplyr::pull()
    
  xdata_test_notarget[[i]] <- xdata_test[[i]] %>% 
    dplyr::select(-target)
  
  caret::postResample(predict(dec_mod[[i]], 
                              xdata_test_notarget[[i]]), 
                      factor(ydata_test[[i]]))
  
}

```

```{r}
prediction_tibble <- list()
prediction_table <- list()
cfm <- list()

for (i in 1:length(dectree_group)){
  prediction_tibble[[i]] <- 
    tibble("target" = ydata_test[[i]],
           "prediction" = predict(dec_mod[[i]], xdata_test_notarget[[i]]))
  
  prediction_table[[i]] <- table(prediction_tibble[[i]])
  
  cfm[[i]] <- as_tibble(prediction_table[[i]])
  
  print(plot_confusion_matrix(cfm[[i]], 
                        target_col = "target", 
                        prediction_col = "prediction",
                        counts_col = "n"))
  
}
```

```{r, fig.height=10, fig.width=15}
for (i in 1:length(dectree_group)){
  rattle::fancyRpartPlot(dec_mod[[i]]$finalModel)
}
```

```{r}
pred_df <- list()
zero_ids <- list()
one_ids <- list()

for (i in 1:length(dectree_group)){
pred_df[[i]] <- data.frame(
  target = as.numeric(factor(ydata_test[[i]])),
  prediction = as.numeric(predict(dec_mod[[i]], xdata_test_notarget[[i]])),
  row.names = rownames(xdata_test_notarget))

pred_df[[i]]$correct_or_not <- pred_df[[i]]$target + pred_df[[i]]$prediction

zero_ids[[i]] <- rownames(pred_df[[i]][pred_df[[i]][, "correct_or_not"] == 2, ])
one_ids[[i]] <- rownames(pred_df[[i]][pred_df[[i]][, "correct_or_not"] == 4, ])

print(paste0(i, ": length of... zero id\'s: ",
       (length(zero_ids[[i]])),
       " | one id\'s: ",
       (length(one_ids[[i]]))))
}
```
# Matti has not walked farther than this.

```{r}
df[zero_ids[[i]], ]
df[one_ids[[i]], ]
```

```{r}
top_features <- rownames(head(varimp_data[[i]]$importance, 10))
# top_features <- c("behaviour_indoors_nonhouseholders", "behaviour_close_contact", "intention_indoor_meeting")
```

```{r}
# df$demographic_gender <- factor(df$demographic_gender)
# df <- data.frame(apply(df, 2, factor))
```

```{r}
# df %<>%
#        mutate_each_(funs(factor(.)),top_features)
# # str(df)
```

```{r}
x <- df[top_features]

y <- factor(df$behaviour_unmasked_bool)

```

```{r}
set.seed(2021)
inTrain <- createDataPartition(y, p = .80, list = FALSE)[,1]

x_train <- x[ inTrain, ]
x_test  <- x[-inTrain, ]

y_train <- y[ inTrain]
y_test  <- y[-inTrain]

colnames(x_train)
```

```{r}
cl <- makePSOCKcluster(10)
registerDoParallel(cl)

set.seed(2021)

# Specify 10 fold cross-validation
ctrl_cv <- trainControl(method = "repeatedcv",
                        search="grid",
                        number = 10,
                        repeats=10,
                        timingSamps = 5,
                        # seeds = c(1:101)
                        )
# Predict income using decision tree
dec_mod <- train(x=x_train,
                 y=y_train,
                    method = "rpartScore",  
                    trControl = ctrl_cv,
                    tuneGrid = expand.grid(
                      cp = seq(0,1,0.1),
                      split = c("abs", "quad"),
                      prune = c("mc", "mr")
                      )

                 )

stopCluster(cl)
```

```{r}
registerDoSEQ()
```

```{r}
# Post prediction
postResample(predict(dec_mod, x_test), y_test)
```

```{r}
prediction_tibble <- tibble("target"=y_test,
       "prediction"=predict(dec_mod, x_test))
prediction_table <- table(prediction_tibble)
cfm <- as_tibble(prediction_table)

```

```{r}
plot_confusion_matrix(cfm, 
                      target_col = "target", 
                      prediction_col = "prediction",
                      counts_col = "n")
                      
                      
```

```{r, fig.height=10, fig.width=15}
fancyRpartPlot(dec_mod$finalModel)
```

```{r}
varImp(dec_mod)
```

```{r}
ggplot(data=df, aes(x=id, y=intention_store, color=demographic_gender)) + geom_point()
```

```{r}
ggplot(data=df, aes(x=id, y=behaviour_indoors_nonhouseholders, color=demographic_gender)) + geom_point()
```

```{r}
dec_mod
```

```{r}
dec_mod$bestTune
dec_mod$finalModel
```
